\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}

\title{GDG Website \textemdash Vision and Product Spec}
\author{GDGoC NEHU}
\date{February 10, 2026}

\begin{document}
\maketitle

\section*{Purpose}
This document describes the vision for the club website as a living community hub. The site is designed to be a center point for members, with ongoing value through events, resources, roadmaps, and project showcases. The goal is to avoid a one-time static website and instead create a platform the community returns to.

\section*{Mission}
Create a centralized, community-first hub that makes it easy to discover, share, and contribute to club activities, knowledge, and projects.

\section*{Audience}
\begin{itemize}[leftmargin=*]
  \item Current club members seeking events, resources, and roadmaps.
  \item Prospective members looking for a clear view of club activity and culture.
  \item Alumni and collaborators who want to follow updates or contribute.
\end{itemize}

\section*{Vision Principles}
\begin{itemize}[leftmargin=*]
  \item \textbf{Living content:} The site stays fresh through updates, not just launches.
  \item \textbf{Community-first:} Members can discover and contribute easily.
  \item \textbf{Clarity over clutter:} Clean information architecture and quick access to core items.
  \item \textbf{Reliable and accessible:} Fast, mobile-friendly, and easy to navigate.
\end{itemize}

\section*{Core Features}
\begin{itemize}[leftmargin=*]
  \item \textbf{Events:} Calendar, upcoming events, registrations, and past event archive.
  \item \textbf{Resources:} Curated guides, tools, links, and learning materials.
  \item \textbf{Roadmaps:} Structured learning paths from beginner to advanced.
  \item \textbf{Project Showcase:} Highlighted projects with images, tags, and progress.
  \item \textbf{Blog/Updates:} Ongoing updates, tutorials, and member stories.
  \item \textbf{Community Links:} Discord, social channels, and contribution entry points.
\end{itemize}

\section*{Content Strategy}
\begin{itemize}[leftmargin=*]
  \item \textbf{Cadence:} Weekly or biweekly updates to keep momentum.
  \item \textbf{Ownership:} Each content area has a designated maintainer.
  \item \textbf{Quality bar:} Short, useful, and consistent posts over long, infrequent updates.
  \item \textbf{Discoverability:} Tags and filters for projects, resources, and roadmaps.
\end{itemize}

\section*{Ease of Use and Content Updates}
\begin{itemize}[leftmargin=*]
  \item \textbf{Admin experience:} Simple, fast workflows for creating events, posts, and projects.
  \item \textbf{Backend support:} A functioning backend will allow quick data updates without code changes.
  \item \textbf{Goal:} Make content updates easy enough for non-developers to manage.
\end{itemize}

\section*{Governance}
\begin{itemize}[leftmargin=*]
  \item \textbf{Roles:} Editor, Reviewer, and Publisher roles to keep content accurate.
  \item \textbf{Review process:} Lightweight review for public-facing posts.
  \item \textbf{Archive policy:} Older events and projects should remain searchable.
\end{itemize}

\section*{MVP Scope}
\begin{itemize}[leftmargin=*]
  \item Home page with hero, featured sections, and clear calls to action.
  \item Projects list with tags and featured items.
  \item Roadmaps list with curated paths.
  \item Blog list with recent posts and detail view.
  \item Team section and community links.
\end{itemize}

\section*{Backend Status and Timeline}
\begin{itemize}[leftmargin=*]
  \item Backend work is almost ready.
  \item With the backend in place, the remaining time needed is reduced.
\end{itemize}

\section*{Success Metrics}
\begin{itemize}[leftmargin=*]
  \item Repeat visits and time on site.
  \item Content update frequency and contributor count.
  \item Event sign-ups and resource usage.
  \item Project submissions and engagement.
\end{itemize}

\section*{Next Steps}
\begin{itemize}[leftmargin=*]
  \item Finalize MVP content owners and update cadence.
  \item Connect the backend to dynamic content sections.
  \item Launch MVP with a clear onboarding path for new members.
\end{itemize}

\end{document}
